### 2018-08-25 results.tex
Word hard wrap 80 col

Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal neutron flux for both initial and equilibrium composition. The neutron flux has the same shape for both compositions but the equilibrium case has a harder spectrum. A significant spectral shift was observed for the central region of the core (zone I) when for the outer region (zone II) it is negligible for fast but notable for thermal neutrons. This neutron flux radial distribution is in a good agreement with original ORNL report \cite{robertson_conceptual_1971}. Overall, spectrum hardening during \gls{MSBR} operation should be carefully studied for designing the reactivity control system.

@@

  \caption{Radial neutron flux distribution for initial and equilibrium fuel salt composition.}

@@

Figure~\ref{fig:breeding_den} shows the neutron capture reaction rate distribution for $^{232}$Th normalized by the total neutron flux for initial and equilibrium states. The distribution reflects the spatial distribution of $^{233}$Th production in the core. The thorium-232 then $\beta$-decays to $^{233}$Pa which is the precursor for $^{233}$U production. Accordingly, this characteristic represents the breeding distribution in the \gls{MSBR} core. Spectral shift does not cause significant changes in power nor in breeding distribution. Even after 20 years of operation, most of the power still is generated in zone I though the majority of $^{233}$Th is produced in zone II.

@@

  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux for both initial and equilibrium fuel salt composition.}

@@

Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated in this work for both initial and equilibrium fuel composition, and compared with original \gls{ORNL} report data \cite{robertson_conceptual_1971}. Uncertainty for each temperature coefficient also appears in Table~\ref{tab:tcoef}. The main physical principle underlying the reactor temperature feedback is an expansion of matterial that is heated. When the fuel salt temperature increases, the density of the salt decreases, but at the same time, the total volume of fuel salt in the core remains constant because it is bounded by the graphite. When the graphite temperature increases, the density of graphite decreases creating additional space for fuel salt. To determine temperature coefficients, the cross section temperatures for fuel and moderator were changed from 900K to 1000K. Three different cases were considered:

@@

In the first case, changes in the fuel temperature only impact fuel density. In this case, the geometry is unchanged because the fuel is a liquid. However, when the moderator heats up, both the density and the geometry change due to thermal expansion of the solid graphite blocks and reflector. Accordingly, the new graphite density was calculated using a linear temperature expansion coefficient of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}. A new geometry input was created based on this information.

>>>>

Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
neutron flux for both initial and equilibrium composition. The neutron flux has 
the same shape for both compositions but the equilibrium case has a harder 
spectrum. A significant spectral shift was observed for the central region of 
the core (zone I) when for the outer region (zone II) it is negligible for fast 
but notable for thermal neutrons. This neutron flux radial distribution is in a 
good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
studied for designing the reactivity control system.

@@

  \caption{Radial neutron flux distribution for initial and equilibrium fuel 
salt composition.}

@@

Figure~\ref{fig:breeding_den} shows the neutron capture reaction rate 
distribution for $^{232}$Th normalized by the total neutron flux for initial and 
equilibrium states. The distribution reflects the spatial distribution of 
$^{233}$Th production in the core. The thorium-232 then $\beta$-decays to 
$^{233}$Pa which is the precursor for $^{233}$U production. Accordingly, this 
characteristic represents the breeding distribution in the \gls{MSBR} core. 
Spectral shift does not cause significant changes in power nor in breeding 
distribution. Even after 20 years of operation, most of the power still is 
generated in zone I though the majority of $^{233}$Th is produced in zone II.

@@

  \caption{$^{232}$Th neutron capture reaction rate normalized by total flux for 
both initial and equilibrium fuel salt composition.}

@@

Table~\ref{tab:tcoef} summarizes temperature effects on reactivity calculated in 
this work for both initial and equilibrium fuel composition, and compared with 
original \gls{ORNL} report data \cite{robertson_conceptual_1971}. Uncertainty 
for each temperature coefficient also appears in Table~\ref{tab:tcoef}. The main 
physical principle underlying the reactor temperature feedback is an expansion 
of matterial that is heated. When the fuel salt temperature increases, the 
density of the salt decreases, but at the same time, the total volume of fuel 
salt in the core remains constant because it is bounded by the graphite. When 
the graphite temperature increases, the density of graphite decreases creating 
additional space for fuel salt. To determine temperature coefficients, the cross 
section temperatures for fuel and moderator were changed from 900K to 1000K. 
Three different cases were considered:

@@

In the first case, changes in the fuel temperature only impact fuel density. In 
this case, the geometry is unchanged because the fuel is a liquid. However, when 
the moderator heats up, both the density and the geometry change due to thermal 
expansion of the solid graphite blocks and reflector. Accordingly, the new 
graphite density was calculated using a linear temperature expansion coefficient 
of 1.3$\times10^{-6}$1/K \cite{robertson_conceptual_1971}. A new geometry input 
was created based on this information.
